### 2021-08-05 paper/paper.tex
partially finished PID section

@@

>>>>

\begin{figure}[!ht]
\centering
  \begin{subfigure}{\linewidth}
    \begin{tikzpicture}[
      font=\footnotesize
      ]
      \begin{axis}[
          xlabel={Polynomial degree},
          ylabel={Time/RHS/DOF {[sec]}},
          width=\textwidth,
          height=0.66\textwidth,
          legend columns=-1,
          % legend to name=place_legend_here,
          legend pos=north west,
          ymin=0.0,
          ymax=2.0e-6,
          grid=major,
        ]
        \addplot[blue, mark=*, solid] % FLUXO, weak form
          table [x index=0, y index=2]{../new_pid_data/pids_mhd_weak.dat};
          \addlegendentry{FLUXO}
        \addplot[red, mark=diamond*, solid] % StructuredMesh, weak form
          table [x index=0, y index=1]{../new_pid_data/pids_mhd_weak.dat};
          \addlegendentry{\trixi}
        \node at (axis cs:13,3.5e-7) {Weak form};

        \addplot[blue, mark=*, dashed] % FLUXO, flux differencing
          table [x index=0, y index=2]{../new_pid_data/pids_mhd_flogor.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=1]{../new_pid_data/pids_mhd_flogor.dat};
        \node [rotate=15] at (axis cs:9,8.2e-7) {Flux differencing};
        \draw (axis cs:9,9.2e-7) -- (axis cs:8.5,10.2e-7);
        \draw (axis cs:9,7.2e-7) -- (axis cs:8.5,5.2e-7);
      \end{axis}
    \end{tikzpicture}%
    \caption{Absolute run times.}
  \end{subfigure}%
  \\
  \begin{subfigure}{\linewidth}
    \begin{tikzpicture}[
      font=\footnotesize
      ]
      \begin{axis}[
          xlabel={Polynomial degree},
          ylabel={Time relative to FLUXO {[-]}},
          width=\textwidth,
          height=0.66\textwidth,
          legend columns=-1,
          legend pos=south west,
          ymin=0.0,
          ymax=1.1,
          ytick={0, 0.2, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1},
          grid=major,
        ]
        \addplot[blue, mark=*, solid, forget plot] % FLUXO, weak form
          table [x index=0, y index=2]{../new_pid_data/pids_mhd_weak_relative.dat};
        \addplot[red, mark=diamond*, solid] % StructuredMesh, weak form
          table [x index=0, y index=1]{../new_pid_data/pids_mhd_weak_relative.dat};
          \addlegendentry{Weak form}

        \addplot[blue, mark=*, dashed, forget plot] % FLUXO, flux differencing
          table [x index=0, y index=2]{../new_pid_data/pids_mhd_flogor_relative.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=1]{../new_pid_data/pids_mhd_flogor_relative.dat};
          \addlegendentry{Flux differencing}
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           different DG discretizations of the 3D ideal MHD equations.}
  \label{fig:PID-MHD}
\end{figure}

@@

\todo{Trixi runs need redone due to further improvements}
